---
title: "P8105 Homework 1"
author: "Grace Liu (gsl2116)"
date: "9/21/2018"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)     # Load tidyverse
```

## Problem 1

Create a data frame comprised of:  
+ A random sample of size 10 from a uniform[0, 5] distribution  
+ A logical vector indicating whether elements of the sample are greater than 2  
+ A (length-10) character vector  
+ A (length-10) factor vector  

```{r p1_data}
set.seed(1)
set_a = tibble(
  sample_runif = runif(10, min = 0, max = 5),
  vec_logic = sample_runif > 2,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(vec_char)
 )
```

#### Calculate means for all variables:
```{r p1_means_test}
mean(set_a$sample_runif)
mean(set_a$vec_logic)
mean(set_a$vec_char)
mean(set_a$vec_factor)
```
Means were not able to be calculated for the character and factor variables, as they are not numeric or logical variables. Means can be calculated for logical variables as TRUE and FALSE are assigned values of 1 and 0.

#### Explicitly converting variables to numeric:
```{r p1_convertnum, results = FALSE}
as.numeric(set_a$vec_logic)
as.numeric(set_a$vec_char)
as.numeric(set_a$vec_factor)
```
It is possible to convert the logical and factor variables to numeric variables. This is because logical variables have numeric values attributed to them (True = 1, False = 0), and factor variables have both character and numerical values associated with them.

#### Convert character variable from character to factor to numeric:
```{r p1_convertchar, results = FALSE}
as.numeric(as.factor(set_a$vec_char))
```
The character variable can successfully be converted to factor and then numeric. Factors are stored as a vector of numeric values and a corresponding set of character values. As such, it is possible for character variables can be converted to factors due to the factor variable's character values. From here, factors can be converted to numeric variables via the factor variable's integer values.

#### Convert factor variable from factor to character to numeric:
```{r p1_convertfactor, results = FALSE}
as.numeric(as.character(set_a$vec_factor))
```
The factor variable can be converted to a character variable, but from here it can *not* be converted to a numeric variable. It is possible for factor variables can be converted to characters due to the factor variable's character values. However, character variables do not have any numeric values and thus the conversion from character to numeric is unsuccessful.

## Problem 2

Create a data frame comprised of:  
+ x: a random sample of size 1000 from a standard Normal distribution  
+ y: a random sample of size 1000 from a standard Normal distribution  
+ A logical vector indicating whether the x + y > 0  
+ A numeric vector created by coercing the above logical vector  
+ A factor vector created by coercing the above logical vector  

```{r p2_data}
set.seed(1)
plot_data = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  plot_logic = x + y > 0,
  plot_factor = as.factor(plot_logic)
)
```
This dataset has `r nrow(plot_data)` rows and `r ncol(plot_data)` columns. The mean of x is `r mean(plot_data$x)`, and the median of x is `r median(plot_data$x)`. The proportion of cases for which the logical vector is TRUE is `r sum(plot_data$plot_logic) / nrow(plot_data)`.

#### Scatterplot of x and y
```{r}
ggplot(plot_data, aes(x = x, y = y, color = plot_logic)) + geom_point()
```

#### Save scatterplot as image
```{r}
ggsave("p8105_hw1_graph.png")
```

