---
title: "p8105_hw1_gsl2116"
author: "Grace Liu"
date: "9/21/2018"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)     # Load tidyverse
```

## Problem 1

Create a data frame comprised of:  
+ A random sample of size 10 from a uniform[0, 5] distribution  
+ A logical vector indicating whether elements of the sample are greater than 2  
+ A (length-10) character vector  
+ A (length-10) factor vector  

```{r p1_data}
set.seed(1)
set_a = tibble(
  sample_runif = runif(10, min = 0, max = 5),
  vec_logic = sample_runif > 2,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(vec_char)
 )
```

#### Calculate means for all variables:
```{r p1_means_test}
mean(set_a$sample_runif)
mean(set_a$vec_logic)
mean(set_a$vec_char)
mean(set_a$vec_factor)
```
Means were not able to be calculated for the character and factor variables, as they are not numeric or logical variables. Means can be calculated for logical variables as TRUE and FALSE are assigned values of 1 and 0.

#### Explicitly converting variables to numeric:
```{r p1_convertnum, results = FALSE}
as.numeric(set_a$vec_logic)
as.numeric(set_a$vec_char)
as.numeric(set_a$vec_factor)
```


#### Convert character variable from character to factor to numeric:
```{r p1_convertchar, results = FALSE}
as.numeric(as.factor(set_a$vec_char))
```


#### Convert factor variable from factor to character to numeric:
```{r p1_convertfactor, results = FALSE}
as.numeric(as.character(set_a$vec_factor))
```

## Problem 2

Create a data frame comprised of:  
+ x: a random sample of size 1000 from a standard Normal distribution  
+ y: a random sample of size 1000 from a standard Normal distribution  
+ A logical vector indicating whether the x + y > 0  
+ A numeric vector created by coercing the above logical vector  
+ A factor vector created by coercing the above logical vector  

```{r p2_data}
set.seed(1)
plot_data = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  plot_logic = x + y > 0,
  plot_factor = as.factor(plot_logic)
)
```
This dataset has `r nrow(plot_data)` rows and `r ncol(plot_data)` columns. The mean of x is `r mean(plot_data$x)`, and the median of x is `r median(plot_data$x)`. The proportion of cases for which the logical vector is TRUE is `r sum(plot_data$plot_logic) / nrow(plot_data)`.

#### Scatterplot of x and y
```{r}
ggplot(plot_data, aes(x = x, y = y, color = plot_logic)) + geom_point()
```

