---
title: "p8105_hw1_gsl2116"
author: "Grace Liu"
date: "9/20/2018"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Problem 1

Create a data frame comprised of:  
+ A random sample of size 10 from a uniform[0, 5] distribution  
+ A logical vector indicating whether elements of the sample are greater than 2  
+ A (length-10) character vector  
+ A (length-10) factor vector  

```{r p1_data}
set.seed(1)
set_a = tibble(
  samp = runif(10, min = 0, max = 5),
  vec_logic = is.logical(samp > 2),
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(vec_char)
 )
```

```{r p1_means_test, include = FALSE}
mean(set_a$samp)          # Mean = 2.757569
mean(set_a$vec_logic)     # Mean = 1 -> Only sort of works, as "True" is given a value of 1.
mean(set_a$vec_char)      # Mean N/A -> Argument is not numeric or logical.
mean(set_a$vec_factor)    # Mean N/A -> Argument is not numeric or logical.
```

Explicitly converting variables to numeric:
```{r p1_convertnum, results = FALSE}
as.numeric(set_a$vec_logic)      # TRUE converted to 1.
as.numeric(set_a$vec_char)       # NAs introduced by coercion.
as.numeric(set_a$vec_factor)     # Factors converted to numbers; able to calculate mean.
```

Convert character variable from character to factor to numeric:
```{r p1_convertchar, results = FALSE}
as.numeric(as.factor(set_a$vec_char))
```

Convert factor variable from factor to character to numeric:
```{r p1_convertfactor, results = FALSE}
as.numeric(as.character(set_a$vec_factor))     # NAs introduced by coercion.
```

## Problem 2

Create a data frame comprised of:  
+ x: a random sample of size 1000 from a standard Normal distribution  
+ y: a random sample of size 1000 from a standard Normal distribution  
+ A logical vector indicating whether the x + y > 0  
+ A numeric vector created by coercing the above logical vector  
+ A factor vector created by coercing the above logical vector  

```{r p2_data}
set.seed(1)
plot_data = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  logical_plot = is.logical(x + y > 0),
  factor_plot = factor(logical_plot)
)
```
This dataset has `r count(plot_data)` observations. The mean of x is `r mean(plot_data$x)`, and the median of x is `r median(plot_data$x)`. The proportion of cases for which the logical vector is TRUE.
